Capabilities, MMIO and Robust Safety

### 2020-05-14 capability-notes/driver-notes/main.tex
Removed lingering 'sem'
Added few notes on how to implement drivers

\begin{mathpar}
  \mprset{vskip=0.5em}
  \inferrule
  { \X{bootSpec}^{\X{sem}}(P,r_0,m_0) \\
  (r_0, m_0, \emptyset) \longrightarrow^* (r, m, t)\\
  }
  {P(t)}
\end{mathpar}

@@

>>>>

\begin{mathpar}
  \mprset{vskip=0.5em}
  \inferrule
  { \X{bootSpec}(P,r_0,m_0) \\
  (r_0, m_0, \emptyset) \longrightarrow^* (r, m, t)\\
  }
  {P(t)}
\end{mathpar}

@@

\subsection{Basics}

\begin{itemize}
\item Define types for traces
\item Create a regular authoritative resource algebra over traces (we can refine this later on)
\item Parameterize everything by the MMIO = Set(Loc)? locations?
\item Formalize traces in the operational semantics $\rightarrow$ choose how we want to formalize MMIO with respect to memory
\item Formalize traces in the state interpretation
\end{itemize}
